\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-05-08 ase20/eval.tex
[ASE] Fill all numbers
[ASE] Updated eval for ES10-3

    ES10-3 &
    String &
    \makecell[l]{Wrong use of the \code{=} operator in {\bf
    StringGetOwnProperty}} &
    \textsf{X} &
    2015-06-01 &
    TBD &
    \multicolumn{1}{c|}{TBD} &
    7 \\\hline

@@

    BigInt-1 &
    Expression &
    \makecell[l]{Using the wrong variable \code{oldvalue} instead of
    \code{oldValue} in \\ {\bf Evaluation} of {\it UpdateExpression}} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    BigInt-2 &
    Number &
    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} in \\ {\bf
    Number::unsignedRightShift}} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    \inred{XX} \\\hline

    BigInt-3 &
    Number &
    \makecell[l]{Unhandling BigInt values in the {\bf Number} constructor} &
    \textsf{O} &
    2019-09-27 &
    2019-11-19 &
    53 days &
    \inred{XX}
  \end{tabular}
\end{table*}

@@

ES10-3 is due to a misuse of the \code{=} operator for numbers.
In abstract algorithms, ``{\it x} = {\it y}'' denotes equality testing
for double-precision 64-bit binary format IEEE 754-2008 values;
thus, \mbox{``+0 = -0''} evaluates to true.  However, to check whether
{\it index} is exactly the same with -0,
{\bf StringGetOwnProperty} used \mbox{``{\it index} = -0''},
which is true even when {\it index} is +0.
It caused seven tests failed.  We proposed a fix, which is
confirmed on April 22, 2020.

@@

    \code{BigInt} &
    4 &
    0 &
    298/326 &
    \inred{207}/207 &
    \inred{18,064}/18,064\\\hline

@@

We checked the extracted semantics from the proposals
by implemented missing parts of the AST-IR translator for
each proposal and checking the semantics with Test262.  All of them
passed all applicable tests except the semantics from the
\code{BigInt} proposal.  It failed for \inred{XX} tests out of 207
applicable tests for the proposal and \inred{XXXX} tests out of
\inred{XXXXX} applicable tests for ES10.

>>>>

    ES10-3 &
    String &
    \makecell[l]{Wrong use of the \code{=} operator in {\bf
    StringGetOwnProperty}} &
    \textsf{X} &
    2015-06-01 &
    2020-05-07 &
    1,802 days &
    7 \\\hline

@@

    BigInt-1 &
    Expression &
    \makecell[l]{Using the wrong variable \code{oldvalue} instead of
    \code{oldValue} in \\ {\bf Evaluation} of {\it UpdateExpression}} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    533 \\\hline

    BigInt-2 &
    Number &
    \makecell[l]{Using {\bf ToInt32} instead of {\bf ToUint32} in \\ {\bf
    Number::unsignedRightShift}} &
    \textsf{X} &
    2019-09-27 &
    2020-04-23 &
    209 days &
    2 \\\hline

    BigInt-3 &
    Number &
    \makecell[l]{Unhandling BigInt values in the {\bf Number} constructor} &
    \textsf{O} &
    2019-09-27 &
    2019-11-19 &
    53 days &
    1
  \end{tabular}
\end{table*}

@@

ES10-3 is due to a misuse of the \code{=} operator for numbers.
In abstract algorithms, ``{\it x} = {\it y}'' denotes equality testing
for double-precision 64-bit binary format IEEE 754-2008 values;
thus, \mbox{``+0 = -0''} evaluates to true.  However, to check whether
{\it index} is exactly the same with -0,
{\bf StringGetOwnProperty} used \mbox{``{\it index} = -0''},
which is true even when {\it index} is +0.
It caused seven tests failed. We proposed a fix accepted on May 8, 2020.
Thus, ES10-3 existed for 1,802 days.

@@

    \code{BigInt} &
    4 &
    0 &
    298/326 &
    196/207 &
    17,539/18,064\\\hline

@@

We checked the extracted semantics from the proposals
by implemented missing parts of the AST-IR translator for
each proposal and checking the semantics with Test262.  All of them
passed all applicable tests except the semantics from the
\code{BigInt} proposal.  It failed for 11 tests out of 207
applicable tests for the proposal and 525 tests out of
18,064 applicable tests for ES10.
